Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Bias correction included.

@@

>>>>

# long_corr_df %>% 
#   group_by(thresh_tests, samp_n_tests, type) %>% 
#   summarise(meanval = mean(value)) %>% 
#   ungroup() %>% 
#   right_join(., thetas[, c(1,3)]) %>% 
#   mutate(thresh_tests = factor(thresh_tests)) -> means_df

par_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(correctiontype = "Parametric") -> corr_a

nonpar_glm %>% 
  mutate(Original = theta_hat - theta,
         Corrected = theta_bar - theta) %>% 
  dplyr::select(thresh_tests, samp_n_tests, Original, Corrected) %>% 
  pivot_longer(cols = c(Original, Corrected), names_to = "type") %>% 
  filter(., !is.infinite(value)) %>% 
  mutate(correctiontype = "Nonparametric") -> corr_b

correction_df <- rbind.data.frame(corr_a, corr_b)

@@

```{r fig.height=10, fig.width=10}

corr_a %>% 
  right_join(., thetas) %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp) +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Long-distance level", y = "Estimated theta", title = corr_a$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_a$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> a

corr_b %>% 
  right_join(., thetas) %>%
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = value, fill = type)) +
  facet_wrap(~labelsamp) +
  geom_boxplot(alpha = 0.9, outlier.shape = NA) +
  geom_point(aes(y = log(theta)), size = 3, shape = 18, color = theta_color, show_guide = FALSE) +
  scale_fill_manual(values = c("grey47", "white"), name = "") +
  labs(x = "Long-distance level", y = "Estimated theta", title = corr_b$correctiontype[1]) +
  theme_bw() +
  scale_y_continuous(limits = quantile(corr_b$value, c(0.1, 0.9))) +
  theme(legend.position = "right") -> b
